R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
add (too poetic?) conclusion paragraph

>>>>

R Markdown is a remarkably powerful tool in the researcher's tool belt. Given a
community of powerful minds contributing to its future, it will only improve in
its ability to reliably reproduce researcher's results with minimal effort. I
imagine a world where reporting standards (like the PhUSE paper formatting) are
defined in an R Markdown template that any researcher or contributor can easily
use or extend as needed. It is the power of an open source community building
quality and reproducible tools that make such a future possible.
